---
title: "Week_3"
author: "Ipek Bensu"
date: "12/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Interpretting results from last week:  

```{r showChoro1}
shiny::includeHTML("./Tableau_ex.html")
```

- Referring to the model WSRs, we expect metro areas to be "orange", and less dense areas to be "blue".
- Miami, Orlando and Jacksonville in FL follow this trend.  
- However, metro areas such as Atlanta in GA are not discernable. Why?  
- Several inland areas in TX and NY that don't seem to be metro areas are discernable. Why?  
- Perhaps compare screenshots from .geojson files or Google maps.  

# To discuss the economic implications of texture, we need to:  

- Collect necessary information  
- Compute building-specific expected annual losses (EAL)  

## Collecting necessary information  

In one folder collect:  

- Your .mat files from last week  
- Files in Hazus/Hazus_mat  
- Files in ACS_DP03/ACS_DP03_mat  
- Files in ACS_DP04/ACS_DP04_mat  
- Files in PUMS/PUMS_mat  
- Files in Census_tracts_neighbors/mat  
- Entire code under Week_3  

## Computing building-specific expected annual losses (EAL)  

Step 1: Running the code  

- In "Command window" (bottom of page), run "index.m"  
- **Similar to last week, you'll need to adjust the "for" loop for your study area.**  

Step 2: Sharing the results  

- **You'll have 6 .mat and 6 .csv files for EALs in each state.**  
- **2 of each are 'EAL' (in $1000 per household).**  
- **2 are 'EAL_PerValue' (normalized by home value).**  
- **2 are 'EAL_PerInc' (normalized by household income).**  
- **Each includes 'Case0' (for an unmitigated building stock) and 'Case1' (for a mitigated building stock).**  
- **Also, each includes 'Hazus' (based on a framework developed by FEMA) and 'New' (based on an updated framework).**  
- Upload to Dropbox :)  

Additional reading on Hazus:  

- On its terrain and wind modeling: [this](https://ascelibrary.org/doi/full/10.1061/%28ASCE%291527-6988%282006%297%3A2%2882%29)  
- On its loss modeling: [this](https://ascelibrary.org/doi/full/10.1061/%28ASCE%291527-6988%282006%297%3A2%2894%29)  
